Two sample $t$ test example using `nycflights13` `flights` data

### 2018-04-11 inst/doc/two_sample_t.Rmd
Update build vignettes

```{r }
fli_small %>%
  # alt: response = arr_delay, explanatory = half_year
  specify(arr_delay ~ half_year) %>%
  hypothesize(null = "independence") %>%
  # calculate(stat = "t") ## Not needed since t is implied
  visualize(method = "theoretical", obs_stat = obs_t, direction = "two_sided")
```

>>>>

```{r }
fli_small %>%
  # alt: response = arr_delay, explanatory = half_year
  specify(arr_delay ~ half_year) %>%
  hypothesize(null = "independence") %>%
  # generate() ## Not used for theoretical
  calculate(stat = "t", order = c("h1", "h2")) %>%
  visualize(method = "theoretical", obs_stat = obs_t, direction = "two_sided")
```
